Estimating the genome-wide contribution of selection to temporal allele frequency change.

### 2019-09-23 manuscript/manuscript.tex
removed vb tags

\title{Estimating the \gc{genome-wide} contribution of selection to temporal allele frequency change.}

@@

\begin{abstract}
% Adaptation can proceed in natural populations and selection experiments over
% very short timescales.
 \gc{Rapid phenotypic adaptation is often observed in natural populations and selection experiments.}
 However, detecting the \gc{impact of this selection} genome-wide is
  difficult, as\gc{such} adaptation often proceeds from standing
  variation \gc{and} selection on \gc{highly} polygenic traits, both of which may leave faint
  genomic signals indistinguishable from a noisy background of genetic drift.
  One promising signal comes from the genome-wide covariance between allele
  frequency changes observable from temporal genomic data, e.g.
  evolve-and-resequence studies. These temporal covariances reflect how the
  change in neutral allele frequency at one timepoint is predictive of the
  changes at later timepoints when there is heritable fitness variation in the
  population, as neutral alleles can remain associated with selected alleles
  over time. Since genetic drift does not lead to temporal covariance, we can
  use these covariances to estimate what fraction of the variation in allele
  frequency change through time is driven by linked selection. Here, we
  reanalyze two \emph{Drosophila simulans} evolve-and-resequence studies, and
  one artificial selection experiment in mice, to quantify the effects of
  linked selection over short timescales using covariance among
  time-points and across replicates. \gc{We estimate that over 20\% {\bf ??} of allele frequency
  change in these experiments is driven by selection.} \gc{Against
  this background of positive genome-wide tmeporal covariances} We also
  identify signals of negative temporal covariance corresponding to reversals
  in the direction of selection for a reasonable proportion of loci over the time
  course of a selection experiment.  Overall, we find that in the three studies
  we analyzed, linked selection has a \gc{large} impact on short-term allele
  frequency dynamics \gc{that is readily distinguishable from} genetic drift.

  %  Additionally, taking advantage of
  %selection on replicated populations, we can estimate the covariance in allele
  %frequency between replicates due to convergent selection
  %\gc{pressures}.

@@

There are numerous examples of rapid phenotypic adaptation
\parencite{Grant2011-wk,Grant2006-hj,Reznick1997-mh,Franks2007-dr} and rapid
genomic evolution in asexual populations
\parencite{Good2017-om,Bennett1990-bc,Baym2016-kh}.  Yet the polygenic nature
of fitness makes detecting the impact selection on genome-wide variation over
short timescales in sexual populations remarkably difficult. This is because
the effect of selection on a polygenic trait (such as fitness) is distributed
across loci in proportion to their effect sizes. This can lead to subtle allele
frequency shifts on standing variation that are difficult to distinguish from
background levels of genetic drift and sampling variance.  However,
increasingly genomic experimental evolution studies with multiple timepoints,
and in some cases multiple replicate populations, are being used to detect
selected loci \parencite{Turner2011-sx,Turner2012-bm} and differentiate modes
of selection \parencite{Burke2010-tz,Barghi2019-qy,Therkildsen2019-zy}.  In
addition these temporal-genomic studies have begun in wild populations, some
with the goal of finding variants that exhibit frequency changes consistent
with fluctuating selection \parencite{Bergland2014-ij,Machado2018-cs}. \vb{In a
  previous paper, we proposed that one useful signal for understanding the
  genome-wide impact of polygenic linked selection detectable from temporal
genomic studies} is the temporal autocovariance in allele frequency changes
\parencite{Buffalo2019-io}.  These covariances are directly estimable from
temporal genomic data and are created when the loci that underly heritable
fitness variation perturb the frequencies of linked neutral alleles; in
contrast, when genetic drift acts alone in a closed population, these
covariances are zero in expectation. Mathematically, temporal covariances are
useful because it is natural to decompose the total variance in allele
frequency change across a set of time intervals into the variances and
covariances in allele frequency change among time intervals.  Furthermore,
biologically, these covariances reflect the extent to which allele frequency
changes in one generation predict changes in another due to a shared fitness
background and shared selection pressures.

@@

While the presence of positive temporal covariances is consistent with linked
selection affecting allele frequencies over time, this measure not easily
interpretable. Additionally, we can quantify the impact of linked selection on
allele frequency change as the ratio of total covariance in allele frequency
change to the total variance in allele frequency change. \vb{We denote the
change in allele frequency as $\Delta p_t = p_{t+1}-p_t$, where $p_t$ is the
allele frequency in generation $t$}. Since the total variation in allele
frequency change can be partitioned into variance and covariance components,
$\var(p_t - p_0) = \sum_{i} \var(\Delta p_i) + \sum_{i \ne j} \cov(\Delta
p_i, \Delta p_j)$, and the covariances are zero when drift acts alone, this is
a lower bound on how much of the variance in allele frequency change is caused
by linked selection \parencite{Buffalo2019-io}. We call this measure $G(t)$, defined as

\begin{align}
  G(t) = \frac{\sum_{i\ne j}^t \cov(\Delta p_i, \Delta p_j)}{\var(p_t - p_0)}
\end{align}
%
\vb{which estimates} the effect of linked selection between the initial
generation $0$ and some later generation $t$, which can be varied to see how
this quantity grows through time. As with the temporal covariances, the study
design of \textcite{Barghi2019-qy} leads our measure $G(t)$ to be even more
conservative, since the temporal covariances within each ten-generation block
between sequenced timepoints are not directly observable, and are not included
in the numerator of $G(t)$. Still, we find a \vb{remarkably strong signal.
Greater} than $20\%$ of total variation in allele frequency change over 60
generations is the result of linked selection.

\vb{Additionally, we looked for a signal of temporal autocovariance in
\textcite{Bergland2014-ij}, a study that collected \emph{Drosophila
melanogaster} through Spring-Fall seasons across three years. With a pattern of
genome-wide fluctuating selection, we might expect a pattern of positive
covariances between similar seasonal changes, and negative covariances between
dissimilar seasonal changes. However, we find no such signal; we discuss this
in more depth in Supplementary Materials Section \ref{bergland-reanalysis}.}

@@

Finally, we observed that in the longest study  we analyzed
\parencite{Barghi2019-qy}, some genome-wide temporal covariances become
negative at future timepoints (see the first two rows in Figure
\ref{fig:figure-1} A). This shows that alleles that were on average going up
initially are later going down in frequency, i.e. that the average direction of
selection experienced by alleles has flipped. This must reflect either a change
in the environment or the genetic background, due to epistatic relationships
among alleles \vb{altered by frequency changes} or recombination breaking up
selective alleles.  Such reversals of selective dynamics could be occurring at
other timepoints but the signal of a change in the direction of selection at
particular loci may be washed out when we calculate our genome-wide average
temporal covariances.  To address this limitation, we calculated the
distribution of the temporal covariances over 100kb genomic windows (Figure
\ref{fig:figure-3}, pooling across all replicates; see Supplementary Figure
\ref{suppfig:barghi-offset-replicate-panels} for individuals replicates). The
covariance of each tile will be noisy, due to sampling and genetic drift, and
the neutral distribution of the covariance is complicated due to linkage
disequilibria (which can occur over long physical distances in E\&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}). To address
this, we have developed a permutation-based procedure that constructs a null
distribution by randomly flipping the signs of the  allele frequency changes
per-genomic window. This destroys the systematic covariances created by linked
selection and creates a sampling distribution of the covariances spuriously
created by neutral genetic drift while preserving the complex dependencies
between adjacent loci created by linkage disequilibrium (see Supplementary
Material Section \ref{supp:empirical-null} for more details on this approach).
This empirical neutral null distribution is conservative in the sense that the
variances of the covariances are wider than expected under drift alone as they
include the effect of selection on the allele frequency change within a
time-interval, just not between time-intervals. We see (Figure
\ref{fig:figure-3} A and B) that windowed temporal covariances between close
timepoints are skewed positive (a heavy right tail), while between more distant
timepoints these windowed temporal covariances tend to shift to become more
negative (a heavy left tail).  We quantified the degree to which the left and
right tails are inflated compared to the null distribution as a function of
time, and see excesses in both tails in Figure \ref{fig:figure-3} C. This
finding is also robust to sign-permuting allele frequency changes on a
chromosome-level, the longest extent that gametic linkage disequilibria can
extend (Supplementary Figure \ref{suppfig:barghi-tailprobs-seqid}). We see a
striking pattern that the windowed covariances not only decay towards zero, but
in fact become negative through time, consistent with many regions in the
genome having had a reversed fitness effect at later timepoints.

@@

Since the seminal analysis of \textcite{Maynard_Smith1974-lc} demonstrating
that diversity is reduced at linked neutral variation as an advantageous
polymorphism sweeps to fixation, over four decades of theoretical and empirical
research has enriched our understanding of linked selection. This work has led
to the discovery of selected genes from genomic signals of hitchhiking
\parencite{Nair2003-tw,Voight2006-rn}, found genome-wide signals of linked
selection
\parencite{Aguade1989-jx,Begun1992-ey,Cutter2010-gi,Andersen2012-bj,Cutter2003-tl}
leading to the development of recurrent hitchhiking \parencite{Stephan1992-jc}
and background selection \parencite{Charlesworth1993-gb} models that attempt
explain this pattern. Since, much attention has focused on quantifying the
impact of background selection \parencite{McVicker2009-ax} and developing
theoretic machinery \parencite{Coop2012-cd} to differentiate the regional
reductions in diversity into those caused by full and partial sweeps, and those
caused by background selection \parencite{Elyashiv2016-vt}. However, as other
models of soft sweeps from standing variation emerged
\parencite{Hermisson2005-hs,Pennings2006-lj}, attention shifted towards
detecting other modes of linked selection \parencite{Pritchard2010-tk}, a more
difficult endeavor \parencite{Przeworski2005-bg} \vb{addressed using} new coalescent
models \parencite{Berg2015-xj} and machine learning methods
\parencite{Schrider2017-yx}. An \vb{alternative} approach to understanding the
genome-wide effects of selection on standing variation, e.g. selection on an
infinitesimal polygenic trait, stems from an early quantitative genetic model
of linked selection \parencite{Robertson1961-ho} and its later developments
(\cite{Santiago1995-hx,Santiago1998-bs}; see also \cite{Barton2000-zg} for a
comparison of these models with classic hitchhiking models). Implicit in these
models is that autocovariance between allele frequency change is created when
there is heritable fitness variation in the population, a signal that can be
readily detected from temporal genomic data \parencite{Buffalo2019-io}. Here,
we provide the first empirical evidence of linked selection acting on standing
variation over very short timescales.

@@

While we must keep in mind that the studies analyzed here were all laboratory
populations and natural selection in the wild will likely differ, overall we
have found that linked selection has a remarkably strong effect for such short
study durations. Depending on how many loci affect fitness, such a strong
effect of linked selection may not be differentiable from genetic drift using
only single contemporary population samples. In this way, temporal data allows
us to sidestep the key problem of detecting selection from standing variation:
that the genomic footprint leaves too soft of a signature to differentiate from
a background of genetic drift. In fact we find that the temporal covariance
signal is detectable even in the most extremely difficult to detect soft sweep
case: polygenic selection on an infinitesimal trait. In our reanalysis of the
\textcite{Castro2019-uk} data, by showing the covariance signal remains even
after excluding the chromosomes containing two large-effect loci, we showed the
covariance signal we detect is indeed driven by polygenic fitness variation
(and confirm a point in the original study that tibiae length, aside from these
two large effect loci, \vb{is a highly polygenic trait).}

@@

One limitation \vb{of these analyses is} that none of the studies we reanalyzed
estimated linkage disequilibria data for the evolved populations. Our theory of
temporal autocovariance tells us that the temporal autocovariances a neutral
site experiences is determined by the product of the expected linkage
disequilibrium and additive fitness variation that persists through the
generations \parencite{Buffalo2019-io}. This leads to a clear prediction:
regions of higher linkage disequilibrium and lower recombination should have
greater temporal autocovariance than regions with lower LD and higher
recombination. Unfortunately, we lack a high-resolution recombination map for
\emph{D. simulans} and while there are LD data for \emph{D. simulans}
\parencite{Signor2018-wg} we did not find a relationship between temporal
covariance and LD.

@@

Thus far, the most comprehensive studies implicating linked selection in
affecting genome-wide diversity have been in \emph{Drosophila}
\parencite{Begun1992-ey,Elyashiv2016-vt,Sattath2011-dr} and
\emph{Caenorhabditis} \parencite{Cutter2003-tl,Cutter2003-tl,Andersen2012-bj},
whereas the evidence for linked selection in plant and yeast species is weak
\parencite{Cutter2013-ba}. Both \emph{Drosophila} and \emph{Caenorhabditis}
have short genetic maps (or in the case of selfing \emph{C.  elegans}, small
effective recombination rates), and large effect population sizes, two factors
predicted to increase the degree to which hitchhiking impacts genome-wide
diversity \parencite{Barton2000-zg}. However, our results here show that even
with small effective population sizes (300, 450, and 45 for the
\textcite{Kelly2019-dc}, and \textcite{Castro2019-uk} studies respectively)
and, in the case of mice, moderately-sized genetic maps (around 14 Morgans;
\cite{Cox2009-hf}), we still see a fairly strong effect of linked selection.
This suggests that while these factors may govern the dynamics of classic
hitchhiking events, they could perhaps play less of a role in polygenic linked
selection. However, with only three cases \vb{analyzed}, further studies on
different taxa are needed.

>>>>

\title{Estimating the genome-wide contribution of selection to temporal allele frequency change.}

@@

\begin{abstract}

 Rapid phenotypic adaptation is often observed in natural populations and
 selection experiments.  However, detecting the impact of this selection
 genome-wide is difficult, since adaptation often proceeds from standing
 variation and selection on highly polygenic traits, both of which may leave
 faint genomic signals indistinguishable from a noisy background of genetic
 drift.  One promising signal comes from the genome-wide covariance between
 allele frequency changes observable from temporal genomic data, e.g.
 evolve-and-resequence studies. These temporal covariances reflect how the
 change in neutral allele frequency at one timepoint is predictive of the
 changes at later timepoints when there is heritable fitness variation in the
 population, as neutral alleles can remain associated with selected alleles
 over time. Since genetic drift does not lead to temporal covariance, we can
 use these covariances to estimate what fraction of the variation in allele
 frequency change through time is driven by linked selection. Here, we
 reanalyze two \emph{Drosophila simulans} evolve-and-resequence studies, and
 one artificial selection experiment in mice, to quantify the effects of linked
 selection over short timescales using covariance among time-points and across
 replicates. We estimate that over 20\% of allele frequency change in these
 experiments is driven by selection in some experiments. Against this
 background of positive genome-wide temporal covariances we also identify
 signals of negative temporal covariance corresponding to reversals in the
 direction of selection for a reasonable proportion of loci over the time
 course of a selection experiment.  Overall, we find that in the three studies
 we analyzed, linked selection has a large impact on short-term allele
 frequency dynamics that is readily distinguishable from genetic drift.

@@

There are numerous examples of rapid phenotypic adaptation
\parencite{Grant2011-wk,Grant2006-hj,Reznick1997-mh,Franks2007-dr} and rapid
genomic evolution in asexual populations
\parencite{Good2017-om,Bennett1990-bc,Baym2016-kh}.  Yet the polygenic nature
of fitness makes detecting the impact selection on genome-wide variation over
short timescales in sexual populations remarkably difficult. This is because
the effect of selection on a polygenic trait (such as fitness) is distributed
across loci in proportion to their effect sizes. This can lead to subtle allele
frequency shifts on standing variation that are difficult to distinguish from
background levels of genetic drift and sampling variance.  However,
increasingly genomic experimental evolution studies with multiple timepoints,
and in some cases multiple replicate populations, are being used to detect
selected loci \parencite{Turner2011-sx,Turner2012-bm} and differentiate modes
of selection \parencite{Burke2010-tz,Barghi2019-qy,Therkildsen2019-zy}.  In
addition these temporal-genomic studies have begun in wild populations, some
with the goal of finding variants that exhibit frequency changes consistent
with fluctuating selection \parencite{Bergland2014-ij,Machado2018-cs}. In a
previous paper, we proposed that one useful signal for understanding the
genome-wide impact of polygenic linked selection detectable from temporal
genomic studies is the temporal autocovariance in allele frequency changes
\parencite{Buffalo2019-io}.  These covariances are directly estimable from
temporal genomic data and are created when the loci that underly heritable
fitness variation perturb the frequencies of linked neutral alleles; in
contrast, when genetic drift acts alone in a closed population, these
covariances are zero in expectation. Mathematically, temporal covariances are
useful because it is natural to decompose the total variance in allele
frequency change across a set of time intervals into the variances and
covariances in allele frequency change among time intervals.  Furthermore,
biologically, these covariances reflect the extent to which allele frequency
changes in one generation predict changes in another due to a shared fitness
background and shared selection pressures.

@@

While the presence of positive temporal covariances is consistent with linked
selection affecting allele frequencies over time, this measure not easily
interpretable. Additionally, we can quantify the impact of linked selection on
allele frequency change as the ratio of total covariance in allele frequency
change to the total variance in allele frequency change. We denote the
change in allele frequency as $\Delta p_t = p_{t+1}-p_t$, where $p_t$ is the
allele frequency in generation $t$. Since the total variation in allele
frequency change can be partitioned into variance and covariance components,
$\var(p_t - p_0) = \sum_{i} \var(\Delta p_i) + \sum_{i \ne j} \cov(\Delta
p_i, \Delta p_j)$, and the covariances are zero when drift acts alone, this is
a lower bound on how much of the variance in allele frequency change is caused
by linked selection \parencite{Buffalo2019-io}. We call this measure $G(t)$, defined as

\begin{align}
  G(t) = \frac{\sum_{i\ne j}^t \cov(\Delta p_i, \Delta p_j)}{\var(p_t - p_0)}
\end{align}
%
which estimates the effect of linked selection between the initial
generation $0$ and some later generation $t$, which can be varied to see how
this quantity grows through time. As with the temporal covariances, the study
design of \textcite{Barghi2019-qy} leads our measure $G(t)$ to be even more
conservative, since the temporal covariances within each ten-generation block
between sequenced timepoints are not directly observable, and are not included
in the numerator of $G(t)$. Still, we find a remarkably strong signal.
Greater than $20\%$ of total variation in allele frequency change over 60
generations is the result of linked selection.

Additionally, we looked for a signal of temporal autocovariance in
\textcite{Bergland2014-ij}, a study that collected \emph{Drosophila
melanogaster} through Spring-Fall seasons across three years. With a pattern of
genome-wide fluctuating selection, we might expect a pattern of positive
covariances between similar seasonal changes, and negative covariances between
dissimilar seasonal changes. However, we find no such signal; we discuss this
in more depth in Supplementary Materials Section \ref{bergland-reanalysis}.

@@

Finally, we observed that in the longest study  we analyzed
\parencite{Barghi2019-qy}, some genome-wide temporal covariances become
negative at future timepoints (see the first two rows in Figure
\ref{fig:figure-1} A). This shows that alleles that were on average going up
initially are later going down in frequency, i.e. that the average direction of
selection experienced by alleles has flipped. This must reflect either a change
in the environment or the genetic background, due to epistatic relationships
among alleles altered by frequency changes or recombination breaking up
selective alleles.  Such reversals of selective dynamics could be occurring at
other timepoints but the signal of a change in the direction of selection at
particular loci may be washed out when we calculate our genome-wide average
temporal covariances.  To address this limitation, we calculated the
distribution of the temporal covariances over 100kb genomic windows (Figure
\ref{fig:figure-3}, pooling across all replicates; see Supplementary Figure
\ref{suppfig:barghi-offset-replicate-panels} for individuals replicates). The
covariance of each tile will be noisy, due to sampling and genetic drift, and
the neutral distribution of the covariance is complicated due to linkage
disequilibria (which can occur over long physical distances in E\&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}). To address
this, we have developed a permutation-based procedure that constructs a null
distribution by randomly flipping the signs of the  allele frequency changes
per-genomic window. This destroys the systematic covariances created by linked
selection and creates a sampling distribution of the covariances spuriously
created by neutral genetic drift while preserving the complex dependencies
between adjacent loci created by linkage disequilibrium (see Supplementary
Material Section \ref{supp:empirical-null} for more details on this approach).
This empirical neutral null distribution is conservative in the sense that the
variances of the covariances are wider than expected under drift alone as they
include the effect of selection on the allele frequency change within a
time-interval, just not between time-intervals. We see (Figure
\ref{fig:figure-3} A and B) that windowed temporal covariances between close
timepoints are skewed positive (a heavy right tail), while between more distant
timepoints these windowed temporal covariances tend to shift to become more
negative (a heavy left tail).  We quantified the degree to which the left and
right tails are inflated compared to the null distribution as a function of
time, and see excesses in both tails in Figure \ref{fig:figure-3} C. This
finding is also robust to sign-permuting allele frequency changes on a
chromosome-level, the longest extent that gametic linkage disequilibria can
extend (Supplementary Figure \ref{suppfig:barghi-tailprobs-seqid}). We see a
striking pattern that the windowed covariances not only decay towards zero, but
in fact become negative through time, consistent with many regions in the
genome having had a reversed fitness effect at later timepoints.

@@

Since the seminal analysis of \textcite{Maynard_Smith1974-lc} demonstrating
that diversity is reduced at linked neutral variation as an advantageous
polymorphism sweeps to fixation, over four decades of theoretical and empirical
research has enriched our understanding of linked selection. This work has led
to the discovery of selected genes from genomic signals of hitchhiking
\parencite{Nair2003-tw,Voight2006-rn}, found genome-wide signals of linked
selection
\parencite{Aguade1989-jx,Begun1992-ey,Cutter2010-gi,Andersen2012-bj,Cutter2003-tl}
leading to the development of recurrent hitchhiking \parencite{Stephan1992-jc}
and background selection \parencite{Charlesworth1993-gb} models that attempt
explain this pattern. Since, much attention has focused on quantifying the
impact of background selection \parencite{McVicker2009-ax} and developing
theoretic machinery \parencite{Coop2012-cd} to differentiate the regional
reductions in diversity into those caused by full and partial sweeps, and those
caused by background selection \parencite{Elyashiv2016-vt}. However, as other
models of soft sweeps from standing variation emerged
\parencite{Hermisson2005-hs,Pennings2006-lj}, attention shifted towards
detecting other modes of linked selection \parencite{Pritchard2010-tk}, a more
difficult endeavor \parencite{Przeworski2005-bg} addressed using new coalescent
models \parencite{Berg2015-xj} and machine learning methods
\parencite{Schrider2017-yx}. An alternative approach to understanding the
genome-wide effects of selection on standing variation, e.g. selection on an
infinitesimal polygenic trait, stems from an early quantitative genetic model
of linked selection \parencite{Robertson1961-ho} and its later developments
(\cite{Santiago1995-hx,Santiago1998-bs}; see also \cite{Barton2000-zg} for a
comparison of these models with classic hitchhiking models). Implicit in these
models is that autocovariance between allele frequency change is created when
there is heritable fitness variation in the population, a signal that can be
readily detected from temporal genomic data \parencite{Buffalo2019-io}. Here,
we provide the first empirical evidence of linked selection acting on standing
variation over very short timescales.

@@

While we must keep in mind that the studies analyzed here were all laboratory
populations and natural selection in the wild will likely differ, overall we
have found that linked selection has a remarkably strong effect for such short
study durations. Depending on how many loci affect fitness, such a strong
effect of linked selection may not be differentiable from genetic drift using
only single contemporary population samples. In this way, temporal data allows
us to sidestep the key problem of detecting selection from standing variation:
that the genomic footprint leaves too soft of a signature to differentiate from
a background of genetic drift. In fact we find that the temporal covariance
signal is detectable even in the most extremely difficult to detect soft sweep
case: polygenic selection on an infinitesimal trait. In our reanalysis of the
\textcite{Castro2019-uk} data, by showing the covariance signal remains even
after excluding the chromosomes containing two large-effect loci, we showed the
covariance signal we detect is indeed driven by polygenic fitness variation
(and confirm a point in the original study that tibiae length, aside from these
two large effect loci, is a highly polygenic trait).

@@

One limitation of these analyses is that none of the studies we reanalyzed
estimated linkage disequilibria data for the evolved populations. Our theory of
temporal autocovariance tells us that the temporal autocovariances a neutral
site experiences is determined by the product of the expected linkage
disequilibrium and additive fitness variation that persists through the
generations \parencite{Buffalo2019-io}. This leads to a clear prediction:
regions of higher linkage disequilibrium and lower recombination should have
greater temporal autocovariance than regions with lower LD and higher
recombination. Unfortunately, we lack a high-resolution recombination map for
\emph{D. simulans} and while there are LD data for \emph{D. simulans}
\parencite{Signor2018-wg} we did not find a relationship between temporal
covariance and LD.

@@

Thus far, the most comprehensive studies implicating linked selection in
affecting genome-wide diversity have been in \emph{Drosophila}
\parencite{Begun1992-ey,Elyashiv2016-vt,Sattath2011-dr} and
\emph{Caenorhabditis} \parencite{Cutter2003-tl,Cutter2003-tl,Andersen2012-bj},
whereas the evidence for linked selection in plant and yeast species is weak
\parencite{Cutter2013-ba}. Both \emph{Drosophila} and \emph{Caenorhabditis}
have short genetic maps (or in the case of selfing \emph{C.  elegans}, small
effective recombination rates), and large effect population sizes, two factors
predicted to increase the degree to which hitchhiking impacts genome-wide
diversity \parencite{Barton2000-zg}. However, our results here show that even
with small effective population sizes (300, 450, and 45 for the
\textcite{Kelly2019-dc}, and \textcite{Castro2019-uk} studies respectively)
and, in the case of mice, moderately-sized genetic maps (around 14 Morgans;
\cite{Cox2009-hf}), we still see a fairly strong effect of linked selection.
This suggests that while these factors may govern the dynamics of classic
hitchhiking events, they could perhaps play less of a role in polygenic linked
selection. However, with only three cases analyzed, further studies on
different taxa are needed.
